Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-27 tex/nusselt_paper.tex
Jeff's comments are bolded to be taken care of in the future

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
error bars are negligible.  \label{fig:ma_v_eps} }
\end{figure}

@@

Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
away from hydrostatic and thermal equilibrium.
Solutions were time-evolved until a long average of Nu showed little
dependence on depth. A linear stability analysis determined that the onset of convection
occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$ were studied.

@@

After appropriately time-averaging the fluxes, a sensible Nu is retrieved.  Nusselt numbers for
all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
pass into the supersonic regime and shocks start to form near the downflows,
that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is negligible.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at low and high Ma. 
At high $\epsilon$, a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra.  In the low $\epsilon$ regime, Nu scalings collapse onto a similar line which is
reminiscent of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
the variance of Nu with depth.
\label{fig:nu_v_ra} }
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. \textbf{All
error bars are negligible.}  \label{fig:ma_v_eps} }
\end{figure}

@@

\textbf{Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
away from hydrostatic and thermal equilibrium}.
Solutions were time-evolved until a long average of Nu showed little
dependence on depth. \textbf{A linear stability analysis determined that} the onset of convection
occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$ were studied.

@@

\textbf{After appropriately time-averaging the fluxes,} a sensible Nu is retrieved.  Nusselt numbers for
all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
pass into the supersonic regime and shocks start to form near the downflows,
that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is negligible.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at low and high Ma. 
At high $\epsilon$, a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra.  In the low $\epsilon$ regime, Nu scalings collapse onto a similar line which is
\textbf{reminiscent} of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
the variance of Nu with depth. \textbf{Identify power law fits on plot, add 2/7 law?}
\label{fig:nu_v_ra} }
\end{figure}
